%-------------------------
% Resume in LaTeX — auto-generated from resume.yaml
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}

% ---------- PAGE STYLE ----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ---------- MARGINS ----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---------- COLORS ----------
\definecolor{accent}{HTML}{2b6cb0}
\definecolor{darktext}{HTML}{1a1a1a}
\definecolor{lighttext}{HTML}{4a4a4a}

% ---------- SECTION FORMATTING ----------
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries\color{accent}
}{}{0em}{}[\color{accent}\titlerule\vspace{-5pt}]

% ---------- CUSTOM COMMANDS ----------
\newcommand{\resumeItem}[1]{
  \item\small\color{darktext}{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darktext}#1} & \small\color{lighttext}#2 \\
      \textit{\small\color{lighttext}#3} & \textit{\small\color{lighttext}#4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{\color{darktext}#1} & \small\color{lighttext}#2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumePubItem}[1]{
  \vspace{-2pt}\item\small\color{darktext}{#1\vspace{-2pt}}
}

\newcommand{\resumeEduSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{darktext}#1} & \small\color{lighttext}#2 \\
      \textit{\small\color{lighttext}#3} & \textit{\small\color{lighttext}#4} \\
    \end{tabular*}\vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\Huge\scshape\color{darktext} Hayk Manukyan} \\[6pt]
  \small
  \faIcon{phone} \, +4915223636116 \quad\faIcon{envelope} \, \href{mailto:haik.manukyan@gmail.com}{haik.manukyan@gmail.com} \quad\faIcon{linkedin} \, \href{https://www.linkedin.com/in/hayk-manukyan-4aab0962/}{linkedin.com/in/hayk-manukyan-4aab0962} \quad\faIcon{github} \, \href{https://github.com/haikmanukyan}{github.com/haikmanukyan}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
  \small\color{darktext}{
    Experienced ML Scientist and Data Scientist with 7+ years of expertise in computer vision, deep learning, and distributed machine learning. Proficient in developing production-grade AI solutions including image generation, face detection, and generative models. Strong background in model training infrastructure, team leadership, and collaborative research environments.
  }

% ---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior ML Scientist}{2022 -- Present}
      {Picsart}{}
      \resumeItemListStart
        \resumeItem{Development of a model training framework for large scale (multi-node) distributed trainings on slurm clusters, intended for a collaborative research and development environment. Experiment tracking, model versioning and evaluation are implemented using mlflow.}
        \resumeItem{Organized team-level collaboration within the framework of the above solution, including code review, documentation and best practices for reproducibility. Managed a small team of engineers for the development and maintenance of the above solution.}
        \resumeItem{Image outpainting (production)}
        \resumeItem{Text-guided image inpainting, layout and text to image generation (research and production optimization)}
        \resumeItem{Text-guided face to video generation (research)}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{2017 -- 2019}
      {Picsart}{}
      \resumeItemListStart
        \resumeItem{Complete solution for face detection, tracking and keypoint detection optimized for mobile devices}
        \resumeItem{Facial filters, effects (Face Swap, Face Morphing, etc.) and AR stickers based on the above solution}
        \resumeItem{Assembly level kernel optimization for image processing for mobile devices (used for style transfer).}
        \resumeItem{Image classification and content based clustering}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% ---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeEduSubheading
      {Master of Science in Computer Science}{2018 -- 2022}
      {Rheinische Friedrich-Wilhelms-Universität Bonn}{}

    \resumeEduSubheading
      {Bachelor of Science in Applied Mathematics and Informatics}{2013 -- 2017}
      {State Engineering University of Armenia}{}

  \resumeSubHeadingListEnd

% ---------- PUBLICATIONS ----------
\section{Publications}
  \begin{itemize}[leftmargin=0.2in]

    \resumePubItem{Hayk Manukyan, Andranik Sargsyan, Barsegh Atanyan, Zhangyang Wang, Shant Navasardyan, Humphrey Shi. \href{https://arxiv.org/abs/2312.14091}{\textbf{HD-Painter: High-Resolution and Prompt-Faithful Text-Guided Image Inpainting with Diffusion Models}}, \emph{ICLR}, 2025}

    \resumePubItem{Marianna Ohanyan, Hayk Manukyan, Zhangyang Wang, Shant Navasardyan, Humphrey Shi. \href{https://arxiv.org/abs/2406.04032}{\textbf{Zero-Painter: Training-Free Layout Control for Text-to-Image Synthesis.}}, \emph{CVPR}, 2024}

    \resumePubItem{Jiayi Guo, Hayk Manukyan, Chenyu Yang, Chaofei Wang, Levon Khachatryan, Shant Navasardyan, Shiji Song, Humphrey Shi, Gao Huang. \href{https://ieeexplore.ieee.org/document/10310257}{\textbf{FaceCLIP: Facial Image-to-Video Translation via a Brief Text Description.}}, \emph{IEEE Transactions on Circuits and Systems for Video Technology}, 2024}

  \end{itemize}

% ---------- PROJECTS ----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{HD-Painter diffusers community pipeline}}{}
      \resumeItemListStart
        \resumeItem{A diffusers implementation of our paper "HD-Painter High-Resolution and Prompt-Faithful Text-Guided Image Inpainting with Diffusion Models".}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Animating Humans with Recurrent Neural Networks (master thesis)}}{}
      \resumeItemListStart
        \resumeItem{Controllable, interactive human animation using recurrent neural networks.}
        \resumeItem{Supervisors: Prof. Dr. Juergen Gall, Dr. Nils Goerke, Julian Tanke}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Detecting And Tracking A Quadcopter Visually (lab project)}}{}
      \resumeItemListStart
        \resumeItem{Optimzed and fast mixed CV and AI solution for detecting and tracking a quadcopter in video sequences in real time.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% ---------- SKILLS ----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages:}{ python, C++, C\#, bash} \\
      \textbf{ML \& AI:}{ opencv, tensorflow, pytorch, pandas, numpy, scipy, mlflow, diffusion, GenAI} \\
      \textbf{Data \& Databases:}{ postgreSQL} \\
      \textbf{Tools \& Platforms:}{ git, docker, slurm, linux, LaTeX}
    }}
  \end{itemize}


\end{document}
